\section*{1. Personal Pronouns}

Fill in the correct personal pronoun:

\begin{enumerate}
  \item My name is Ben. \rule{2cm}{0.15mm} am 11 years old.
  \item This is Sarah. \rule{2cm}{0.15mm} is my friend.
  \item Peter and I play football. \rule{2cm}{0.15mm} are in the same team.
  \item Look at the dog. \rule{2cm}{0.15mm} is very cute.
  \item Where is Tom? Have you seen \rule{2cm}{0.15mm}?
\end{enumerate}

---

\section*{2. \textit{to be} and \textit{to have}}

Fill in the correct form of \textbf{to be} or \textbf{to have}:

\begin{enumerate}[resume]
  \item I \rule{2cm}{0.15mm} twelve years old.
  \item They \rule{2cm}{0.15mm} a big house.
  \item We \rule{2cm}{0.15mm} from Germany.
  \item She \rule{2cm}{0.15mm} a brother and a sister.
  \item He \rule{2cm}{0.15mm} hungry.
\end{enumerate}

---

\section*{3. Simple Present – Positive, Negative, Question}

\textbf{A)} Write the correct form in the simple present:

\begin{enumerate}[resume]
  \item Sarah (play) \rule{3cm}{0.15mm} the piano.
  \item We (watch) \rule{3cm}{0.15mm} TV in the evening.
  \item He (not like) \rule{3cm}{0.15mm} bananas.
  \item (you / go) \rule{3cm}{0.15mm} to school by bike?
  \item My parents (work) \rule{3cm}{0.15mm} in a hospital.
\end{enumerate}

---
\newpage
\section*{4. Vocabulary}

Translate the following words into English:

\begin{multicols}{2}
\begin{enumerate}[resume]
  \item Hund \dotfill
  \item Schule \dotfill
  \item spielen \dotfill
  \item groß \dotfill
  \item Wochenende \dotfill
\end{enumerate}
\end{multicols}

---

\section*{5. Reading Comprehension}

\textbf{Read the text and answer the questions:}

\textit{My name is Emma. I am 12 years old and I live in London. I have a little brother called Max. He is 8 years old. We have a dog. His name is Bruno. I go to Greenfield School and my favourite subject is English. I like reading and playing tennis.}

\begin{enumerate}[resume]
  \item How old is Emma? \dotfill
  \item What is her brother’s name? \dotfill
  \item Do they have a pet? \dotfill
  \item What is Emma’s favourite subject? \dotfill
  \item What does she like to do? \dotfill
\end{enumerate}

---

\section*{6. Creative Task}

Write 5 sentences about yourself. Use the simple present.  
Example: “I live in … / I like … / I go to …”
