\section{Grammar – Wiederholung und Übungen}

\subsection{Zeitformen}
Setze die Verben in die richtige Zeitform:
\begin{enumerate}
    \item Yesterday, I (go) \underline{\hspace{3cm}} to the cinema with my friends.
    \item By the end of next year, she (finish) \underline{\hspace{3cm}} her studies.
    \item While we (walk) \underline{\hspace{3cm}} in the park, it suddenly started to rain.
    \item He (live) \underline{\hspace{3cm}} in London for five years now.
    \item If I (have) \underline{\hspace{3cm}} more time, I would learn another language.
\end{enumerate}

\subsection{Passiv}
Setze die Sätze ins Passiv:
\begin{enumerate}
    \item They built the bridge in 1990. \\
          \underline{\hspace{3cm}}
    \item Someone stole my bike last night. \\
          \underline{\hspace{3cm}}
    \item They will publish the book next month. \\
          \underline{\hspace{3cm}}
\end{enumerate}

\subsection{Indirect Speech}
Setze die Sätze in die indirekte Rede um:
\begin{enumerate}
    \item She said: "I will help you." \\
          \underline{\hspace{3cm}}
    \item Tom asked: "Where do you live?" \\
          \underline{\hspace{3cm}}
\end{enumerate}

\subsection{If-Clauses}
Vervollständige die Sätze mit der passenden Bedingung:
\begin{enumerate}
    \item If I had studied more, \underline{\hspace{3cm}}.
    \item If it rains tomorrow, \underline{\hspace{3cm}}.
    \item If she \underline{\hspace{3cm}}, she would be happier.
\end{enumerate}

\section{Vocabulary and Writing}

\subsection{Übersetze die Sätze ins Englische:}
\begin{enumerate}
    \item Ich bin seit drei Jahren in dieser Schule.
    \item Sie sagte, dass sie morgen anrufen würde.
    \item Wenn er mehr Geld hätte, würde er eine Weltreise machen.
    \item Dieses Buch wurde 1995 veröffentlicht.
\end{enumerate}

\subsection{Textproduktion}
Schreibe einen kurzen Text (100–150 Wörter) zu einem der folgenden Themen:
\begin{itemize}
    \item The advantages and disadvantages of social media
    \item My dream job and why I want to do it
    \item A trip that changed my life
\end{itemize}