% --- English Worksheet: 7th Grade Essentials ---

\section*{English – Essential Topics}

\subsection*{1. Tenses}
\textbf{A) Fill in the correct tense (Simple Present, Present Progressive, Simple Past, will-future):}
\begin{enumerate}[a)]
    \item I usually (go) \rule{2cm}{0.15mm} to school by bike.
    \item Right now, she (read) \rule{2cm}{0.15mm} a book.
    \item Last year, we (visit) \rule{2cm}{0.15mm} London.
    \item Tomorrow, they (play) \rule{2cm}{0.15mm} football.
\end{enumerate}

\subsection*{2. Question Formation}
\textbf{B) Make questions:}
\begin{enumerate}[a)]
    \item you / like / pizza
    \item she / go / to school / yesterday
    \item they / play / tennis / now
    \item he / visit / his grandma / next week
\end{enumerate}

\subsection*{3. Negation}
\textbf{C) Make negative sentences:}
\begin{enumerate}[a)]
    \item I play football.
    \item She is reading a book.
    \item They went to the cinema.
    \item We will visit Paris.
\end{enumerate}

\subsection*{4. If-Clauses (Type I and II)}
\textbf{D) Complete the sentences:}
\begin{enumerate}[a)]
    \item If it rains, I \rule{2cm}{0.15mm} (stay) at home.
    \item If I had a dog, I \rule{2cm}{0.15mm} (walk) it every day.
    \item If you study, you \rule{2cm}{0.15mm} (pass) the test.
    \item If I were you, I \rule{2cm}{0.15mm} (not / do) this.
\end{enumerate}

\subsection*{5. Vocabulary}
\textbf{E) Translate into English:}
\begin{enumerate}[a)]
    \item Hausaufgaben
    \item Lieblingsessen
    \item Freundschaft
    \item Wochenende
    \item Urlaub
\end{enumerate}

\subsection*{6. Reading Comprehension}
\textbf{F) Read the text and answer the questions:}

\textit{Tom is twelve years old. He lives in London with his parents and his little sister. Every morning, he takes the bus to school. His favourite subject is Maths, but he also likes English. In his free time, Tom plays football and reads adventure books.}

\begin{enumerate}[a)]
    \item How old is Tom?
    \item Where does he live?
    \item How does he get to school?
    \item What is his favourite subject?
    \item What does he do in his free time?
\end{enumerate}

\subsection*{7. Grammar: Parts of Speech}
\textbf{G) Mark the nouns, verbs, adjectives and adverbs in the following sentences:}
\begin{enumerate}[a)]
    \item The quick brown fox jumps over the lazy dog.
    \item She sings beautifully.
    \item My best friend is very tall.
    \item They always do their homework carefully.
\end{enumerate}

\subsection*{8. Writing}
\textbf{H) Write a short text (5-7 sentences) about your last holiday. Use at least two different tenses.}

\subsection*{9. Everyday Situations}
\textbf{I) What would you say in these situations?}
\begin{enumerate}[a)]
    \item You want to buy a ticket for the bus.
    \item You don’t understand something in class.
    \item You want to order food in a restaurant.
    \item You meet someone for the first time.
\end{enumerate}

\subsection*{10. Sentence Structure}
\textbf{J) Put the words in the correct order:}
\begin{enumerate}[a)]
    \item always / breakfast / I / have / at / seven o’clock
    \item to school / by bike / goes / she / every day
    \item last week / we / a test / wrote
    \item English / like / I / very much
\end{enumerate}
