\section*{1. Simple Present and Simple Past}

Complete the sentences with the correct form of the verb in brackets. Use either the \textbf{Simple Present} or \textbf{Simple Past}.

\begin{enumerate}
    \item She \_\_\_\_\_\_\_\_ (play) soccer every day.
    \item Yesterday, we \_\_\_\_\_\_\_\_ (visit) the zoo.
    \item They \_\_\_\_\_\_\_\_ (go) to the park every Saturday.
    \item Last night, I \_\_\_\_\_\_\_\_ (watch) a movie.
    \item He always \_\_\_\_\_\_\_\_ (eat) breakfast at 7 AM.
\end{enumerate}

\vspace{0.5cm}

\section*{2. Present Progressive and Past Progressive}

Fill in the blanks with the correct form of the verb in brackets. Use either the \textbf{Present Progressive} or \textbf{Past Progressive}.

\begin{enumerate}
    \item Right now, they \_\_\_\_\_\_\_\_ (run) to school.
    \item While I \_\_\_\_\_\_\_\_ (read) a book, the phone rang.
    \item We \_\_\_\_\_\_\_\_ (study) English at the moment.
    \item She \_\_\_\_\_\_\_\_ (sleep) when the alarm went off.
    \item At this time yesterday, I \_\_\_\_\_\_\_\_ (write) a letter.
\end{enumerate}

\vspace{0.5cm}

\section*{3. Present Perfect and Past Perfect}

Use the correct form of the verb in brackets. Choose either \textbf{Present Perfect} or \textbf{Past Perfect}.

\begin{enumerate}
    \item She \_\_\_\_\_\_\_\_ (finish) her homework before dinner.
    \item They \_\_\_\_\_\_\_\_ (live) in London for five years.
    \item By the time we arrived, the movie \_\_\_\_\_\_\_\_ (start).
    \item I \_\_\_\_\_\_\_\_ (never/see) such a beautiful painting before.
    \item He \_\_\_\_\_\_\_\_ (already/leave) when we got to the party.
\end{enumerate}

\vspace{0.5cm}

\section*{4. Mixed Tenses}

Put the verbs in brackets in the correct tense (Simple Present, Simple Past, Present Progressive, Past Progressive, Present Perfect, or Past Perfect).

\begin{enumerate}
    \item When I \_\_\_\_\_\_\_\_ (get) home yesterday, my brother \_\_\_\_\_\_\_\_ (already/go) to bed.
    \item I \_\_\_\_\_\_\_\_ (study) English since I was a child.
    \item They \_\_\_\_\_\_\_\_ (work) at the company when the boss \_\_\_\_\_\_\_\_ (arrive).
    \item She \_\_\_\_\_\_\_\_ (play) the piano right now.
    \item He \_\_\_\_\_\_\_\_ (never/be) to Australia before.
\end{enumerate}

\vspace{0.5cm}

\section*{5. Ordering Events}

Rearrange the words to form correct sentences. Be careful with the tenses!

\begin{enumerate}
    \item already / eaten / she / has / lunch.\\
    \textbf{Correct Sentence:} \underline{\hspace{10cm}}
    
    \item reading / while / I / was / the book / the phone rang.\\
    \textbf{Correct Sentence:} \underline{\hspace{10cm}}
    
    \item arrived / had / they / the movie / when / started / already.\\
    \textbf{Correct Sentence:} \underline{\hspace{10cm}}
    
    \item playing / were / soccer / they / when / it / started / raining.\\
    \textbf{Correct Sentence:} \underline{\hspace{10cm}}
    
    \item studying / for / she / the exam / two hours / has / been.\\
    \textbf{Correct Sentence:} \underline{\hspace{10cm}}
\end{enumerate}