% --- Aufgabenblatt: English Tenses (9th Grade) ---

\section*{English Tenses – Aufgabenblatt}

\subsection*{1. Simple Present vs. Present Progressive}
\begin{enumerate}[a)]
    \item I usually \underline{\hspace{2cm}} (go) to school by bike, but today I \underline{\hspace{2cm}} (take) the bus.
    \item She \underline{\hspace{2cm}} (read) a book right now.
    \item My parents \underline{\hspace{2cm}} (work) every day from 8 to 5.
    \item Listen! The birds \underline{\hspace{2cm}} (sing).
    \item We \underline{\hspace{2cm}} (not/play) football at the moment.
\end{enumerate}

\subsection*{2. Simple Past vs. Past Progressive}
\begin{enumerate}[a)]
    \item While I \underline{\hspace{2cm}} (do) my homework, my brother \underline{\hspace{2cm}} (watch) TV.
    \item They \underline{\hspace{2cm}} (walk) to school when it \underline{\hspace{2cm}} (start) to rain.
    \item What \underline{\hspace{2cm}} you \underline{\hspace{2cm}} (do) at 7 o'clock yesterday?
    \item I \underline{\hspace{2cm}} (break) my leg while I \underline{\hspace{2cm}} (ski).
    \item She \underline{\hspace{2cm}} (not/listen) when the teacher \underline{\hspace{2cm}} (ask) her a question.
\end{enumerate}

\subsection*{3. Present Perfect vs. Simple Past}
\begin{enumerate}[a)]
    \item I \underline{\hspace{2cm}} (never/be) to London.
    \item He \underline{\hspace{2cm}} (finish) his homework two hours ago.
    \item \underline{\hspace{2cm}} you ever \underline{\hspace{2cm}} (eat) sushi?
    \item We \underline{\hspace{2cm}} (live) here since 2019.
    \item She \underline{\hspace{2cm}} (just/arrive) at the station.
\end{enumerate}

\subsection*{4. Will-Future vs. Going-to-Future}
\begin{enumerate}[a)]
    \item Look at those clouds! It \underline{\hspace{2cm}} (rain).
    \item I think our team \underline{\hspace{2cm}} (win) the match.
    \item We \underline{\hspace{2cm}} (visit) our grandparents next weekend. (plan)
    \item I \underline{\hspace{2cm}} (help) you with your homework. (spontaneous)
    \item They \underline{\hspace{2cm}} (move) to Berlin next year. (decision made before)
\end{enumerate}

\subsection*{5. Mixed Tenses}
Fill in the correct tense (Simple Present, Present Progressive, Simple Past, Past Progressive, Present Perfect, Will-Future, Going-to-Future):
\begin{enumerate}[a)]
    \item When I \underline{\hspace{2cm}} (come) home yesterday, my mother \underline{\hspace{2cm}} (cook) dinner.
    \item I \underline{\hspace{2cm}} (not/see) him since last week.
    \item She \underline{\hspace{2cm}} (study) for her test at the moment.
    \item If it \underline{\hspace{2cm}} (rain) tomorrow, we \underline{\hspace{2cm}} (stay) at home.
    \item My friends \underline{\hspace{2cm}} (play) football every Saturday.
    \item He \underline{\hspace{2cm}} (already/do) his homework.
    \item While we \underline{\hspace{2cm}} (walk) in the park, we \underline{\hspace{2cm}} (meet) an old friend.
    \item I \underline{\hspace{2cm}} (go) to the cinema tonight. (plan)
\end{enumerate}

\subsection*{6. Translate into English}
\begin{enumerate}[a)]
    \item Ich habe meine Hausaufgaben schon gemacht.\hspace{1cm} 
    \item Während sie las, klingelte das Telefon.\hspace{1cm} 
    \item Wir werden morgen unsere Großeltern besuchen.\hspace{1cm} 
    \item Sie spielt gerade Klavier.\hspace{1cm} 
    \item Hast du jemals Sushi gegessen?\hspace{1cm} 
\end{enumerate}

\subsection*{7. Creative Writing}
Write a short story (10 to 15 sentences) using at least three different tenses from above.

% --- End of worksheet ---
